\documentclass{article}
\usepackage[pdftex]{hyperref}

\makeatletter
\renewcommand{\abstractname}{Instructions}
\makeatother

\renewcommand{\arraystretch}{1.5}

\title{MAT -- 112: Group Evaluation\\
\large{Group 1}}
\date{April 30, 2018}

\begin{document}
\maketitle

\begin{abstract}
Please provide an honest evaluation of each of your group members, including yourself, on the following categories. Each category should receive a rating from $1$ to $5$, where $1$ denotes no contribution, $2$ minimal contribution, $3$ average contribution, $4$ above average contribution, and $5$ denotes maximal contribution.  Your rating may be based upon, but not limited to, the descriptions of each category below. You may fill out the table on the second page in most PDF viewers (Adobe Reader, Preview, etc.) and return the saved file to me via email, or you may print out the file fill it out in pen and return to my office. 
\end{abstract}

\paragraph*{Attendance:} Did the group member show up to all designated meeting times, barring reasonable circumstances?
\paragraph*{Research:} Was the group member involved in research by find resources, collecting data, analyzing data, etc.?
\paragraph*{Presentation:} Was the group member involved in the presentation by putting together slides, notecards, the outline, or giving feedback while your group rehearsed their presentation?
\paragraph*{Topic Choice:} Was the group member involved in choosing the topic by providing ideas, finding resources, or discussing the topic with the instructor?
\paragraph*{Overall:} How easy was it to work with the group member, did they have a positive attitude, was their work and attitude conducive to the fulfillment of the project, did they limit distractions during the group's work time?

\newpage

\textbf{Your Name:}~\TextField[name=name,width=7cm,charsize=12pt]{\mbox{}}

\vspace*{2em}

\begin{Form}
   
\begin{tabular}{c | c | c | c | c | c | c}
& Attendance & Research & Presentation & Topic Choice & Overall\\
\hline
Katie & \TextField[name=A1,width=1cm]{\null} & \TextField[name=R1,width=1cm]{\null} & \TextField[name=P1,width=1cm]{\null} & \TextField[name=T1,width=1cm]{\null} & \TextField[name=O1,width=1cm]{\null} \\
\hline \\
Maria & \TextField[name=A2,width=1cm]{\null} & \TextField[name=R2,width=1cm]{\null} & \TextField[name=P2,width=1cm]{\null} & \TextField[name=T2,width=1cm]{\null} & \TextField[name=O2,width=1cm]{\null} \\
\hline \\
Claire & \TextField[name=A3,width=1cm]{\null} & \TextField[name=R3,width=1cm]{\null} & \TextField[name=P3,width=1cm]{\null} & \TextField[name=T3,width=1cm]{\null} & \TextField[name=O3,width=1cm]{\null}  \\
\hline \\
Olivia & \TextField[name=A4,width=1cm]{\null} & \TextField[name=R4,width=1cm]{\null} & \TextField[name=P4,width=1cm]{\null} & \TextField[name=T4,width=1cm]{\null} & \TextField[name=O4,width=1cm]{\null} \\
\hline \\
\end{tabular}
 
\end{Form}
   
 \end{document}