\documentclass{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{enumerate}
\usepackage{pgfplots}

\makeatletter
\renewcommand{\abstractname}{Instructions}
\makeatother

\pgfplotsset{holdot/.style={color=blue,fill=white,only marks,mark=*}}

\title{MAT -- 112: Calculus I and Modeling\\
\large{Review 2 and Final Project}}
\author{Instructor: Thomas R. Cameron}
\date{March 12, 2018}

\begin{document}
\maketitle

\begin{abstract}
 This handout is intended to prepare you for our upcoming review and final project. 
\end{abstract}

\paragraph*{Review 2.} Our second review will be handed out on Wednesday March 14 and will be due in class on Monday March 19. The topics include continuity, derivatives, derivative rules, and applications. You should review everything from Sections 3.1 -- 5.2.

\paragraph*{Final Project.} Our final project presentations will be during the week of 4/30 -- 5/4 and you should begin thinking about them now. First, you must find a group of $3$ or at most $4$. Second, you must pick a topic that relates to our course and notify me as soon as possible of your choice. Potential topics are listed below.
\begin{itemize}
\item	Any of the material from Sections 9.1 -- 9.5, 13.1 -- 13.3, and 14.1 -- 14.3.
\item	Any applications of the material we covered to the life or physical sciences (e.g. see the Extended Applications at the end of each chapter).
\item	Any other topic of your choosing, with my approval. 
\end{itemize}
\end{document}